### 2017-04-21 sections/math.tex
Update on Overleaf.

% TODO: Singular Value Decomposition in general
% TODO: Describe how to calculate decomposition of arbitrary matrix with example
% TODO: add more citations separated by comma

@@

@@

% TODO: Singular values and norms of matrix

@@

\subsection{Randomized SVD}
In \cite{Holmes2007, Candes2011, Woolfe2008, Martinsson2011} are described randomized algorithms for constructing approximate matrix factorizations. Their main purpose is to accelerate calculations of matrix decompositions which tend to be very slow for large data sets.

% TODO: add citation with description of algorithm: \cite{Halko2011}

% TODO: tenhle odstavec vyhodit
Exact SVD of a $m \times n$ matrix has time complexity $O(min(mn^2, m^2n))$ using the "big-O" notation. Assume the data points are in the columns of $\mtrx{A}$ where $m \leq n$. Note that $\mtrx{AA^\mathsf{T}}$ is the dataset covariance matrix. Then a simple method is to randomly choose $k<m$ columns of $\mtrx{A}$ that form a matrix $\mtrx{B}$. Statistically, the SVD of $\mtrx{BB^\mathsf{T}}$ will be close to that of $\mtrx{AA^\mathsf{T}}$; thus it suffices to calculate the SVD of $\mtrx{B}$, the complexity of which, is only $O(k^2m)$.
% see: http://mathoverflow.net/questions/161252/what-is-the-time-complexity-of-truncated-svd

>>>>

% Singular Value Decomposition in general
% TODO: Describe how to calculate decomposition of arbitrary matrix with example

@@

Exact SVD of a $m \times n$ matrix has time complexity $O(min(mn^2, m^2n))$ using the "big-O" notation. In \cite{Holmes2007, Candes2011, Woolfe2008, Martinsson2011} are described randomized algorithms for constructing approximate matrix factorizations that have better asymptotic complexity. Their main purpose is to accelerate calculations of matrix decompositions which tend to be very slow for large data sets.

@@

@@
